---
title: "Review"
author: "Ann Murithi"
date: "3/18/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```
My comments: 
1. All your code run well to produce the expected files. 
2. Good job with the file insepection
3. Creating of file path and saving of your data was creative to reduce long unnecessary file paths. 
4. Placing the output of the analysis into individual folders made your work accessible and easy to follow
5. Overall, your work was well done with every step clearly explained from file inspection, processing to visualization.
 
Good job!
```
--> I would only suggest that you move your comments outside of the script chunk. For each of the step, you would make the comments either before or after the chunk. 
Here is an example for insepction of the SNP_file

#SNP_Position Analyzing File Structure

  1. Use file.info function to determine file size.
  2. dim function returns the dimension of the dataframe. 
  3. ncol function determines number of columns in dataframe. 
  4. names function to determine the coulumn headers in snp_position.txt dataframe
  5. head function returns the first 6 lines of the snp_poisition.txt dataframe
  6. tail function returns the last 6 lines of the snp_position.txt dataframe

```{r}
snp_position.txt=read.csv("snp_position.txt")
file.info("snp_position.txt")$size 
snp_position.txt=(as.data.frame=(read.table("snp_position.txt", sep= "\t", header= TRUE)))
dim(snp_position.txt) 
ncol(snp_position.txt) 
names(snp_position.txt)
head(snp_position.txt, n=6L, addrownames=TRUE) 
tail(snp_position.txt, n=6L, addrownames=TRUE) 
```